---
output:
  word_document: default
  html_document: default
---
One-way ANOVA Analysis to test the hypothesis of 'AI Usage can decrease artistic creativity'

*Loading Libraries*

```{r}
library(DescTools)
library(psych)
library(ggplot2)
library(dplyr)
library(car)
library(effectsize)
library(RcmdrMisc)
library(tidyverse)
library(rstatix)
library(ggpubr)
options(es.use_symbols = TRUE)
knitr::opts_chunk$set(echo = TRUE)
library(text2vec)
library(tm)
library(SnowballC)
library(glmnet)
library(vip)
library(naivebayes)
library(ranger)
library(xgboost)
library(ROCR)
```

################################################################################

*Loading the Dataset*

```{r}
dataname<-read.csv("AI_Survey.csv")
```


*Data Cleaning for further analysis.*
```{r}
cleanedData <- dataname[!dataname=="",]

```


```{r}
#Converting required columns to numeric values 
cleanedData$DQ1_12 <- as.numeric(cleanedData$DQ1_12)
typeof(cleanedData$DQ1_12)
cleanedData$DQ1_13 <- as.numeric(cleanedData$DQ1_13)
typeof(cleanedData$DQ1_13)
cleanedData$DQ1_15 <- as.numeric(cleanedData$DQ1_15)
typeof(cleanedData$DQ1_15)
cleanedData$DQ1_16 <- as.numeric(cleanedData$DQ1_16)
typeof(cleanedData$DQ1_16)
cleanedData$DQ1_17 <- as.numeric(cleanedData$DQ1_17)
typeof(cleanedData$DQ1_17)
cleanedData$Q9_4 <- as.numeric(cleanedData$Q9_4)
typeof(cleanedData$Q9_4)
cleanedData <- na.omit(cleanedData)
```


```{r}
#Creating a column for outcome variable measurement
cleanedData$Creativity <- rowSums(cleanedData[ , c(3:7)], na.rm=TRUE)
```


```{r}
#Removing the first row
#cleanedData <- cleanedData[-c(1),]
#View(cleanedData)
```


```{r}
#Cleaning the poem column
cleanedData$AI.Usage <- tolower(cleanedData$AI.Usage)
cleanedData$AI.Usage <- gsub("[[:punct:]]", "", cleanedData$AI.Usage)
cleanedData<- cleanedData[str_count(cleanedData$AI.Usage, "\\S+") > 3,]
words_to_remove = c("chatgpt|chat gpt")

cleanedData  <- subset(cleanedData, !grepl(words_to_remove, cleanedData$AI.Usage))
cleanedData <- na.omit(cleanedData)
#cleanedData <- cleanedData[cleanedData$Q9_4 != "",]
#View(cleanedData)

```


################################################################################
*Descriptive statistics*

```{r}
library(RcmdrMisc)
numSummary (cleanedData$Creativity, groups=cleanedData$Condition, statistics=c("mean", "sd"))
```



################################################################################

Since our predictor is a factor, we need to make sure R recognizes it as such.

```{r}
cleanedData$Condition <- as.factor(cleanedData$Condition)
```

*Running an independent t-test to check if the manipulation of independent variable worked*

1) Assumption of Independent Observations*
- Each observation is independent so this is not violated.

2) Assumption of an Approximately Normally Distributed Outcome Variable

```{r}
plot(density(cleanedData$Creativity))
```


3) Assumption of Homogeneity of Variance

```{r}
cleanedData$Condition <- as.factor(cleanedData$Condition)
leveneTest(cleanedData$Creativity~cleanedData$Condition)


# This assumption is not violated IF p > 0.05.
```


4) Assumption of No Outliers or Extreme Scores

```{r}
boxplot(cleanedData$Creativity)
```


***Did the manipulation actually work?***


```{r}
t.test(cleanedData$Q9_4~cleanedData$Condition, var.equal=TRUE)

```
Actual p = 0.05/2 = 0.02 as the difference between group 1 and group 2 was predicted in the same direction as per the results.

An independent samples t-test showed that there was not a significant difference (t(34)= 2.01, p = 0.02) between the group which didn't use ChatGPT (M = 252.1053, SD=94.15525) compared to the group that used ChatGPT (M = 277.4706, SD=82.71118 ).


################################################################################

*Assessing Data for ANOVA*


```{r}
#Data points in each group


length(cleanedData$Condition[cleanedData$Condition==1])
length(cleanedData$Condition[cleanedData$Condition==2])

```


```{r}
#Factoring the predictor/independent variable since it is categorical
cleanedData$Condition <- as.factor(cleanedData$Condition) 
```


Testing Assumptions for ANOVA:
*Assumption #1: No Extreme Outliers*

```{r}
boxplot(cleanedData$Creativity~cleanedData$Condition, data=cleanedData)
```
There is one outlier in Group 1 where the participants were asked to write a poem on there own without external help. Therefore this assumption is violated.

*Assumption #2: Homogeneity of Variances*

```{r}

library(car)
leveneTest(cleanedData$Creativity ~ cleanedData$Condition)


# This assumption is not violated IF p > 0.05.
```

*Assumption #3: Normality*

```{r}
regression <- aov(lm(Creativity~Condition, data=cleanedData))
plot(regression, 2)

```


################################################################################

*Analysis for effect of AI Usage on artistic creativity using one way ANOVA*
```{r}
#dataname$Condition <- as.factor(dataname$Condition)
#dataname$SubjectVariable <- as.factor(dataname$SubjectVariable)

model1 <- aov(lm(Creativity~Condition, data=cleanedData))
summary(model1)

```

################################################################################

*Graph to plot the results*


```{r}
library(ggplot2)

ai_creativity <-ggplot(cleanedData, aes(x=Condition, y=Creativity)) + geom_boxplot() + labs(title="Impact of AI usage on Creativity",x="Usage of AI (ChatGPT)", y = "Artistic Creativity") + 
scale_x_discrete(breaks=c("1","2"), labels=c("ChatGPT NOT used to write a poem", "ChatGPT Used to write a poem")) 

ai_creativity
```

In the above graph it is observed that the group which used AI (ChatGPT) scored higher on K-DOCS which goes against the researcher's hypothesis. The result from one-way ANOVA shows that there is no significant impact of AI usage on creativity (p=0.39), therefore we fail to reject the null hypothesis. Based on the results of this study it can be concluded that usage of AI tools such as ChatGPT cannot cause a decrease in a person's ability to write a short poem.




