
Using Pearson's R to find the correlation between AI usage and artistic creativity. It is hypothesized that higher scores on AI usage scale will negatively correlate with higher scores on creativity scale. 

Load the Libraries 

```{r}
library(DescTools)
library(psych)
library(ggplot2)
library(dplyr)
```


Loading Your Dataset:

```{r}
surveydata <- read.csv("TASurvey.csv")

```

Cleaning the dataset
```{r}
#Removing unnecessary columns from the dataset
surveydata <- surveydata[-c(1:17)]
surveydata <- surveydata[-c(10)]
```


```{r}

```


```{r}
#Changing all columns to numeric type
surveydata$CTQ_1 <- as.numeric(surveydata$CTQ_1)
surveydata$CTQ_3 <- as.numeric(surveydata$CTQ_3)
surveydata$CTQ_10 <- as.numeric(surveydata$CTQ_10)
surveydata$Q4_6 <- as.numeric(surveydata$Q4_6)
surveydata$PPB_12 <- as.numeric(surveydata$PPB_12)
surveydata$PPB_13 <- as.numeric(surveydata$PPB_13)
surveydata$PPB_15 <- as.numeric(surveydata$PPB_15)
surveydata$PPB_16 <- as.numeric(surveydata$PPB_16)
surveydata$PPB_17 <- as.numeric(surveydata$PPB_17)
```
```{r}
#Removing Na values
surveydata <- na.omit(surveydata)
```


Reviewing your Dataset
```{r}
describeBy(surveydata)
```


```{r}
#Creating predictor and outcome columns to measure them
surveydata$Predictor <- rowSums(surveydata[ , c(1:4)], na.rm=TRUE)
surveydata$Outcome <- rowSums(surveydata[ , c(5:9)], na.rm=TRUE)
```


Creating vectors for easier understanding of code

```{r}
predictor<- surveydata$Predictor
outcome<- surveydata$Outcome
```

Examining Statistical Assumptions

```{r}
plot(density(predictor))
plot(density(outcome))

ggplot(surveydata, aes(x=predictor, y=outcome)) + geom_point() + geom_jitter() + ggtitle("Correlation between predictor and outcome") + labs(y=" outcome", x = "predictor")
```

Running the Inferential Analysis:
```{r}
#Pearson's R to find correlation between predictor and outcome
cor.test(predictor,outcome) 
```


Graph to visualize the results

```{r}
ggplot(surveydata, aes(x=predictor, y=outcome)) + geom_point() + geom_jitter() + ggtitle("Correlation analysis between AI usage and Creativity") + labs(y=" Creativity", x = "AI Usage")
```


From the above results it can be concluded that there is statistically insignificant weak positive correlation (r(26)=0.34, p=0.06) between scores on AI usage scale and scores on K-DOCS. 






